EDA

### 2024-12-03 other/EDA/EDA.qmd
deleted redundant data

>>>>

```{r fig-template96}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: template
#| fig-align: center

#TODO Fix colors and supplier names and order of supps (highest to lowest)
View(aggregated_df)

# Create the bar chart with legend removed
ggplot(aggregated_df, aes(x = reorder(word, total_amount), y = total_amount, fill = buyer)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(
    title = "Top 10 Suppliers by Aggregated Amount Awarded",
    x = "Supplier",
    y = "Total Amount Awarded"
    # Remove the legend title by not specifying 'fill' in labs
  ) +
  theme_minimal() +
  theme(legend.position = "right")
